Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-21 prop_letter.tex
prop_letter.tex \section{Born rule and Gleason's Theorem} Updating...

Although a THOS rule have many desirable properties, the set of intervals
it mapping to either is trivial or contains infinite intervals.

@@

Since $\iota$ maps to intervals, we can decompose it into two functions:
its left-end and right-end $\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992}.
It is well-known that a Wright-convex function is midpoint-convex
or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
i.e., we have
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
\end{equation}
Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
the left-end function~$\iotal$ must be continuous on the unit open
interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
Therefore, either $\iota$ maps every number in $\left(0,1\right)$
to the same interval, or the number of intervals that $\iota$ maps
to must be uncountable.

>>>>

Although a THOS rule has many desirable properties, the set of intervals
it mapping to either is trivial or contains infinite intervals.

@@

Since $\iota$ maps to intervals, we can decompose it into two functions:
its left-end and right-end $\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
By Eq.~(\ref{eq:iota-Inclusion}), the left-end function $\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-convex~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992},
i.e., 
\begin{equation}
\begin{aligned} & \iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\\
\ge{} & \iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)\,.
\end{aligned}
\end{equation}
Then, for any $x_{0}'$ and $x_{1}'\in\left[0,1\right]$, we can substitute
$x_{0}$ and $x_{1}$ by $\left(x_{0}'-x_{1}'\right)/2$ , substitute
$x_{2}$ by $x_{1}'$, and get the following inequality 
\begin{eqnarray}
\frac{\iotal\left(x_{0}'\right)+\iotal\left(x_{1}'\right)}{2} & \ge & \iotal\left(\frac{x_{0}'+x_{1}'}{2}\right)\,,
\end{eqnarray}
i.e., $\iotal$ is midpoint-convex or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992}.
Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
the left-end function~$\iotal$ must be continuous on the unit open
interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}.
Therefore, either $\iota$ maps every number in $\left(0,1\right)$
to the same interval, or the number of intervals that $\iota$ maps
to must be uncountable.
